Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-05-20 supplement/05_calibration_data.Rmd
res patch using smoothed speed

First, we filter data where we know the animal spent some time at or near a position, as this is the first step to identify residence patches. 
One way of doing this is to filter out positions with speeds above which the animal is likely to be in transit, but a better way of doing this by filtering on a metric such as residence time [@bracis2018].

### Calculate residence time

First we calculate the residence time with a radius of 50 metres.
For this, we need a dataframe with coordinates, the timestamp, and the animal id.
We save this data to file for later use.

```{r}
# get 4 column data
data_for_patch <- data_thin[, list(x, y, time, TAG)]

# get recurse data for a 10m radius
recurse_stats <- getRecursions(data_for_patch,
  radius = 50, timeunits = "mins"
)

# assign to recurse data
data_for_patch[, res_time := recurse_stats$residenceTime]

@@

We subset data with a residence time > 5 minutes in order to construct residence patches.
From this subset, we construct residence patches using the parameters: `buffer_radius` = 5 metres, `lim_spat_indep` = 50 metres, `lim_time_indep` = 5 minutes, and `min_fixes` = 3.

@@

# on known residence points
patch_res_known <- atl_res_patch(data_for_patch[res_time >= 5, ],
  buffer_radius = 5,
  lim_spat_indep = 50,
  lim_time_indep = 5,
  min_fixes = 3
)
```

>>>>

First, we filter data where we know the animal (or in this case, the human-carried tag) spent some time at or near a position, as this is the first step to identify residence patches. 
One way of doing this is to filter out positions with speeds above which the tag (ideally on an animal) is likely to be in transit.
Rather than filtering on instantaneous speed estimates, filtering on a median smoothed speed estimate is more reliable.

### Exclude transit points

Here, we aim to remove locations where the tag is clearly moving, by filtering on smoothed speed, using a one-way median smooth with $K$ = 5.
The speeds between points must be recalculated here because the speed metrics now associated with the data refer to the raw data before median smoothing.

```{r}
# get 4 column data
data_for_patch <- copy(data_thin)

# recalculate speeds, removing speed out
data_for_patch[, c("speed_in", "speed_out") := list(
  atl_get_speed(data_for_patch),
  NULL
)]

# get smoothed speed
data_for_patch[, speed_smooth := runmed(speed_in, k = 5)]

@@

We subset data with a smoothed speed < 2 m/s in order to construct residence patches.
From this subset, we construct residence patches using the parameters: `buffer_radius` = 5 metres, `lim_spat_indep` = 50 metres, `lim_time_indep` = 5 minutes, and `min_fixes` = 3.

@@

# on known residence points
patch_res_known <- atl_res_patch(
  data = data_for_patch[speed_smooth < 2, ],
  buffer_radius = 5,
  lim_spat_indep = 50,
  lim_time_indep = 5,
  min_fixes = 3
)
```
